Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-14 paper/paper.tex
finish section on separable scattering, cite schadler

Considering the separable scattering gives a performance of $\textbf{91\%} \pm 4.5$.
% TODO VL: write about frequency-depedendent time shift. cite IEEE TSP
% TODO VL: insist on the role of modulations in playing techniques.

>>>>

Yet, despite its greater simplicity, separable time--frequency scattering suffers from known weaknesses in its ability to represent spectrotemporal modulations.
In particular, a previous publication has shown that frequency-dependent time shifts affect joint time--frequency scattering coefficients while leaving separable time--frequency scattering coefficients almost unchanged \cite{anden2019tsp}.
For this reason, separable time--frequency scattering coefficients can only serve to recognize periodic modulations (e.g. vibrato), but joint time--frequency scattering is required to recognize pitch evolution-based techniques (PETs, e.g. glissando) \cite{wang2020icassp}.
The same observation was made by \cite{schadler2015jasa} in the case of separable Gabor filterbank features (GBFB), which bear some resemblance with separable time--frequency scattering.

Over our cohort of $K=31$ subjects, separable time--frequency scattering achieves a precision at rank five (P@5) of $\textbf{91.9\%} \pm 4$. This figure is noticeably worse than joint time--frequency scattering, all other things being equal.
